The impact of gas bulk rotation on the Lyman $\alpha$ line

### 2014-04-26 paper/ms.tex
fig size
updated FWHM section

The central results of this paper are evident in Figures
\ref{fig:CentralSpec} and \ref{fig:HomSpec}. They show 2D histograms
of escape frequency $x$ and escape angle $\theta$ parameterized by
$|\mu|$ after verifying that the solutions are symmetric with respect to
$\mu=0$.  Making a selection around a given value of $\mu$ gives us the
line detected by an observer located at an angle $\theta$ with respect
to the rotation axis.

@@

There are three clear effects on the line's morphology as the
rotational velocity increases. First, the line broadens; second, the
double peaks reduce their intensity; and third, the intensity at the
line center rises. The last two effects merge to give the
impression that the double peaks are merger into one at high rotational
velocities, a result that is evident for the homogeneously distributed
sources as shown in the dashed lines of Figure
\ref{fig:differentvelocities}.

In

@@

We consider possible variations in the integrated flux with respect to
$\theta$.

We define the flux by:
\begin{equation}
F(\mu) = \frac{2\Delta N}{N\Delta \mu}, 
\end{equation}

Where $\mu=\cos\Theta$, $N$ is the total number of outgoing photons,
$\Delta N$ is the number of photons in an angular bin $\Delta
\Theta$. This definition satisfies the condition
$\int_{-1}^{1}F(\mu)d\mu/2=1$.  With this definitions, the 
emission is characterized by a flat $F(\mu)$ distribution as 
is shown in \ref{fig:muhisto}, this means that the amount of flux
is the same for all of the angles.

We

@@

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.8\textwidth]{widths.eps}
\end{center}
  \caption{FWHM for the non-dusty models as a function of
    rotational velocity $V_{\rm max}$. The left panel shows the
    results in velocity units while the right panel normalizes
    the data by the FWHM in the static case. 
    Continuous (dashed) lines  correspond to central (homogeneous)
    source distributions. The straight lines represent the fit to
    the data using the expression in Eq. (\ref{eq:fwhm}).
    \label{fig:widthvsmu}} 
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.8\textwidth]{f2.eps}
\end{center}
\caption{Position of the peak maxima as a function of rotational
  velocity $V_{\rm max}$. Continuous (dashed) lines correspond to
  central (homogeneous) source distributions. A value of $x_{\rm
    max}=0$ indicates that line becomes single
  peaked. \label{fig:widthsvsvelocity}}  
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.8\textwidth]{maxima.eps}
\end{center}
\caption{Position of the peak maxima as a function of rotational
  velocity $V_{\rm max}$. Continuous (dashed) lines correspond to
  central (homogeneous) source distributions. A value of $x_{\rm
    max}=0$ indicates that line becomes single
  peaked. \label{fig:maximumsvsvelocity}}  
\end{figure*}

We use the full width at half maximum (FWHM) to quantify the line
broadening. For this we measure the width by interpolating dots in 
our spectra this would produce a continuous spectra which makes easier
to find the half maximum in our histogram numerically, just finding the 
values of the width at the half maximum. In Figure \ref{fig:widthvsmu}
the effect of the viewing angle is shown, the main effects here are that 
as $\mu$ increase the FWHM decrease this is also explained by the same argument
of section XX. The second effect is that clearly as $\rm{V_{max}}$ increase 
the FWHM also increase.

 Figure \ref{fig:widthvsvelocity} shows how the FWHM increases
with rotational velocity both for the central (continuous lines) an 
homogeneous (dashed lines) sources, for $\theta=\pi/2$.
 We parametrize the dependency of the line width with
$V_{\rm max}$ as
\begin{equation}
 {\rm FWHM}^2 = {\rm FWHM}_{0}^2 + V_{\rm max}^2/\lambda^2,
\label{eq:fwhm}
\end{equation}
%
where FWHM$_{0}$ is the velocity width in the static case and $\lambda$ 
is a positive scalar to be determined as a fit to the data. 
With this test we want to know
to what extent the new velocity width can be expressed as a quadratic
sum of the two relevant velocities in the problem. We fit
simultaneously all the points corresponding to central and homogeneous
models to find $\lambda_{\rm c} = 3.89 \pm 0.04$ and $\lambda_{\rm h}=
1.98\pm 0.06$ respectively.

\subsection{Peaks Positions}
\label{sec:peaks}

>>>>

The central results of this paper are summarized in Figures
\ref{fig:CentralSpec} and \ref{fig:HomSpec}. They show 2D histograms
of the escape frequency $x$ and outgoing angle $\theta$ parameterized by
$|\mu|$. Constructing the emission line with photons around a value
of $\mu$ would gives us the emission detected by an observer located at an
angle $\theta$ with respect to the rotation axis. We have veryfied
that the solutions are indeed symmetric with respect to $\mu=0$.

@@

For this case of $|\mu|\sim 0$, there are three clear effects on the
line's morphology as the rotational velocity increases. First, the
line broadens; second, the double peaks reduce their intensity; and
third, the intensity at the line center rises. The last two effects
merge to give the impression that the double peaks are merged into one
at high rotational velocities, a result that is evident for the
homogeneously distributed sources as shown in the dashed lines of
Figure \ref{fig:differentvelocities}.

@@

@@

We consider possible variations in the integrated flux with respect to
$\theta$. We define the normalized flux seen by an observer at an
angle $\mu$ by: \begin{equation}
F(\mu) = \frac{2\Delta N}{N\Delta \mu}, 
\end{equation} 
%
where $\mu=\cos\Theta$, $N$ is the total number of outgoing photons,
$\Delta N$ is the number of photons in an angular bin $\Delta
\Theta$. This definition satisfies the condition
$\int_{-1}^{1}F(\mu)d\mu/2=1$.

Figure \ref{fig:muhisto} shows a flat $F(\mu)$ for all models. It
means that in spite of the different morphologies, the integrated flux
is the same for all sight angles.

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.95\textwidth]{widths.eps}
\end{center}
  \caption{FWHM for the non-dusty models as a function of the viewing
  angle parameterized by $\mu\equiv\cos\theta$. 
  Continuous (dashed) lines  correspond to central (homogeneous)
  source distributions. The general trend is of an decreasing FWHM as
  the line of sight becomes parallel to the rotation axis. 
  \label{fig:widthvsmu}} 
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.95\textwidth]{f2.eps}
\end{center}
\caption{FWHM for the non-dusty models as a function of
  rotational velocity $V_{\rm max}$. The left panel shows the
  results in velocity units while the right panel normalizes
  the data by the FWHM in the static case. 
  Continuous (dashed) lines  correspond to central (homogeneous)
  source distributions. The straight lines represent the fit to
  the data using the expression in Eq. (\ref{eq:fwhm}).
  \label{fig:widthsvsvelocity}}
\end{figure*}

We use the full width at half maximum (FWHM) to quantify the line
broadening. We measure this width from the velocity histogram by
finding the values of the velocities at half maximum. We use linear
interpolation between histogram points to get a more precise value for
this width.

Figure \ref{fig:widthvsmu} shows the FWHM for all models as a function
of the viewing angle. The FWHM increases for decreasing values of
$\mu$ increases and increasing values of $V_{\rm max}$. In Figure
\ref{fig:widthvsvelocity} we fix $|\mu|<0.1$ and show the FWHM as a
function of rotational velocity. For this case we parametrize the
dependency of the line width with  $V_{\rm max}$ as

\begin{equation}
 {\rm FWHM}^2 = {\rm FWHM}_{0}^2 + V_{\rm max}^2/\lambda^2,
\label{eq:fwhm}
\end{equation}
%
where FWHM$_{0}$ is the velocity width in the static case and $\lambda$ 
is a positive scalar to be determined as a fit to the data.

With this test we want to know to what extent the new velocity width
can be expressed as a quadratic sum of the two relevant velocities in
the problem. We fit simultaneously all the points corresponding to
central and homogeneous models to find $\lambda_{\rm c} = XX \pm
XX$ and $\lambda_{\rm h}= XX\pm XX$ respectively.

\subsection{Line Maxima}
\label{sec:peaks}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.95\textwidth]{maxima.eps}
\end{center}
\caption{Position of the line maxima as a function of rotational
  velocity $V_{\rm max}$. Continuous (dashed) lines correspond to
  central (homogeneous) source distributions. A value of $x_{\rm
    max}=0$ indicates that line becomes single
  peaked. \label{fig:maximumsvsvelocity}}  
\end{figure*}
